---
title: "NCBI repositories and FAIR criteria"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("/Users/jan/Documents/OneDrive - Charité - Universitätsmedizin Berlin/_BIH/BUA-Dashboards/fair-assessment")
source("R/07_charts_ncbi.R")
```

## Open Research Data by Charité scientists in 2020

For 2020, `r length(unique(data$article))` research articles written by Charité scientists were identified that shared the underlying research data freely in a data repository. Of these 300 articles, `r data %>% filter(str_detect(best_identifier, "ncbi")) %>% distinct(article) %>% nrow()` used one or more NCBI repositories to share data. [Gene Expression Omnibus](https://www.ncbi.nlm.nih.gov/geo/) in particular is a frequently used repository by Charité scientists. 88 articles have shared research data in this repository.

```{r}
bar_ncbi

# Dump: Highlight Rmd text
# ==highlight==
# <mark>Marked text</mark>
# <mark style="background-color: #b6d5e0">Marked text</mark>
```



## NCBI repositories and completeness of FAIR criteria

The analysis of published research data included an assessment of FAIR criteria completeness (FAIR score) using automated assessment tools like [F-UJI](https://www.f-uji.net). 

```{r}
bar_ncbi_perc
```

## FAIR principles

The last chart shows the FAIR scores broken down by the four main FAIR principles (Findable, Accessible, Interoperable, Reusable) and grouped by NCBI repositories, other field-specific repositories, and general-purpose repositories.

```{r, out.width="100%"}
bar_ncbi_fair
```

```{r}
# Text Dump

# For 2020, `r length(unique(data$article))` research articles written by Charité scientists were identified that shared the underlying research data freely in a data repository. Of these 300 articles, <mark style="background-color: #c1207533;">`r data %>% filter(str_detect(best_identifier, "ncbi")) %>% distinct(article) %>% nrow()` used one or more NCBI repositories</mark> to share their data. [Gene Expression Omnibus](https://www.ncbi.nlm.nih.gov/geo/) in particular is a frequently used repository by Charité scientists. 88 articles have shared their research data in this repository.

# The analysis of published research data included a qualitative assessment of FAIR criteria completeness using automated assessment tools like [F-UJI](https://www.f-uji.net). The analysis demonstrated that <mark style="background-color: #c1207533;">the NCBI repositories do not meet the FAIR criteria. They achieve an overall score of 4.2%</mark> just by passing the test "Identifier is resolvable and follows a defined unique identifier syntax (IRI, URL)". All other FAIR tests failed.

# While field-specific repositories generally show a low completeness of FAIR criteria, there are examples that score better. (For example [the Electron Microscopy Data Bank](https://www.ebi.ac.uk/emdb/) or [CodeOcean](https://codeocean.com).)

# The last chart shows the FAIR scores broken down by the four main FAIR principles (Findable, Accessible, Interoperable, Reusable) and grouped by NCBI repositories, other field-specific repositories, and general-purpose repositories. It demonstrates that NCBI repositories only partly fulfill the Findable principle and completely fail on the other principles, whereas the general-purpose repositories on average also achieve high to medium scores on these principles.
```

